### 2020-06-29 README.Rmd
update conduct, tidymodels resources

We welcome others helping us make this package as user-friendly and efficient as possible. Please review
our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines. Please see the open [issues](https://github.com/tidymodels/infer/issues) for more specific fixes/additions needing attention. By participating in this project you agree to abide by its terms.

>>>>

We welcome others helping us make this package as user-friendly and efficient as possible. Please review our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines. By participating in this project you agree to abide by its terms.

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/tune/issues). Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
